Preprints in Ecology \& Evolution

### 2012-08-28 ms.tex
Small edits

\author{Timoth\'ee Poisot}
\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}

@@

@@

While the practice is still rare, preprints are becoming more common in
biological sciences, which is experiencing faster growth in arXiv submission
than any other fields \cite{cal12}. Also, most scientific journals are
preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly), and all the
journals from Elsevier and Springer. Very recently, the Ecological Society of
America recently changed its policy to allow public preprints (REF). In our
field, very few scientific publications will not consider a manuscript submitted
to arXiv. Many ecology \& evolution journals hostile to preprints are from
Wiley-Blackwell, which has no official policy on the subject. Ecology Letters,

% A table?

>>>>

@@

\author{Timoth\'ee Poisot}
\affiliation{Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Canada.}
\affiliation{Quebec Center for Biodiversity Science, McGill University, Canada.}
\affiliation{International Network for Next-Generation Ecology.}

@@

While the practice is still rare, preprints are becoming more common in
biological sciences, which is experiencing faster growth in arXiv submission
than any other fields \cite{cal12}. Also, most scientific journals are
preprint-friendly: Nature, PLOS, BMC, PNAS, Science (mostly), and all the
journals from Elsevier and Springer. Very recently, the Ecological Society of
America recently changed its policy to allow public preprints (REF). In our
field, very few scientific publications will not consider a manuscript
submitted to arXiv. Many ecology \& evolution journals adopt a ``by default''
hostile attitude towards preprints, mostly due to the lack of clear policy of
the publishers. As an example, Wiley-Blackwell, which publishes some of the
leading journal in the field (a quick lsit), has no official policy on the
subject.

% A table?
%% Journal | Publisher | ISI rank | Official policy ?
